### 2016-01-30 AssignmentXI/Assignment10-Ditz_Schroeder-WS15-16.tex
aufgabe 2 ist fertig

>>>>

The probability whether a unitig is unique can be done with a formula derived from the Lander-Waterman 
model for shotgun sequencing. This formula is
\begin{equation}
 \frac{e^{-c} c^k}{k!}\text{, with } c = \frac{\rho R}{L} \nonumber
\end{equation}
for non-oversampled unitigs and
\begin{equation}
 \frac{e^{-2c} (2c)^k}{k!} \nonumber
\end{equation}
for unitigs that are the result of collapsing two repeats. In these formulas $R$ is the number of reads, $L$ is the length 
of target sequence, $\rho$ is the length of the unitig and $k$ is the number of reads contained by the 
unitig.

In this task we consider a source sequence of length $L = 2Mb$ and $R = 22000$ reads. The length of 
the unitig is $\rho = 3000bp$ and it consists of $k = 100$ reads. With the formulas mentioned above, the 
probability of this specific unitig to be unique is
\begin{equation}
 \frac{e^{-\frac{3000 \cdot 22000}{3000000}} \cdot (\frac{3000 \cdot 22000}{3000000})^{100}}{100!} \approx 5.221 \cdot 10^{-34} \nonumber
\end{equation}
for the case that our unitig is not oversampled and 
\begin{equation}
 \frac{e^{-2\frac{3000 \cdot 22000}{3000000}} \cdot (2\frac{3000 \cdot 22000}{3000000})^{100}}{100!} \approx 1.846 \cdot 10^{-13} \nonumber
\end{equation}
for the case that our unitig is the result of collapsing to repeats.
